A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-04-19 jacobian_calc_CMAME.tex
made own drawing of truss

\subsection{Second example and related studies} 
\label{subsec:Validation}
The second program,a \emph{NRComparison.cpp}, follows a case study that appears in \cite{rezaiee2010dynamic}. The example program departs from the cited literature by applying each of CS, AD and FD and verifying them against an analytical model of a nonlinear mechanical system involving a connected beam and spring. Fig. \ref{fig:TrussSchematic} is a schematic of the beam and spring system. 
%
\begin{figure}[tbp] \centering \includegraphics[width=0.7\textwidth]{./figs/truss.png}
\caption{Beam and spring simulated in example program.} \label{fig:TrussSchematic}
\end{figure}
%
The equations describing this system and results for verification were obtained
in \cite{rezaiee2010dynamic}. They include a force function, Eqn.
\ref{eqn:TrussForce}, and an analytical force derivative or stiffness, Eqn.
\ref{eqn:TrussStiffness}.

>>>>

\subsection{Second example and related studies} 
\label{subsec:Validation}
The second program,a \emph{NRComparison.cpp}, follows a case study that appears in \cite{rezaiee2010dynamic}. The example program departs from the cited literature by applying each of CS, AD and FD and verifying them against an analytical model of a nonlinear mechanical system involving a connected beam and spring. Fig. \ref{fig:TrussSchematic} is a schematic of the beam and spring system. 
%
\begin{figure}[tbp] 
\centering %%\includegraphics[width=0.7\textwidth]{./figs/truss.png}

\begin{tikzpicture}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{calc}
\usetikzlibrary{patterns}

\tikzstyle{wall}=[fill,pattern=north east lines,draw=none,minimum width=0.2cm,minimum height=5.1cm];
\tikzstyle{ground}=[fill,pattern=north east lines,draw=none,minimum width=6.1cm,minimum height=.2cm];

\coordinate (bar_1) at (0,0);
\coordinate (bar_1_support) at (0,-.5);

\coordinate (bar_2) at (5,3);
\coordinate (bar_2_pin) at (5.4,3.0);
\coordinate (spring_1_support) at (5,-.5);
\coordinate (spring_1_pin) at (5,0);

\coordinate (rhm) at (5.4,1.5);
\coordinate (rhml) at (4.5,1.5);
\coordinate (mf) at (2.5, -0.8);
\coordinate (lm) at (1.0, 0.0);
\coordinate (mm) at (1.2, 0.0);
\coordinate (rht) at (5.0, 4.0);
\coordinate (rhtt) at (5.0, 4.2);

\node (wall_slider) at (bar_2_pin) [circular sector, draw, rotate=180] {};
\node (ground_triangle_1) at (bar_1_support) [isosceles triangle, draw, rotate=90] {};
\node (ground_triangle_2) at (spring_1_support) [isosceles triangle, draw, rotate=90] {};

\node (wall) at ($ (rhm) !.3cm!(10, 3) $)  [rectangle, draw, style=wall] {};
\node (ground) at (mf)  [rectangle, draw, style=ground] {};

\node (spring_label) at (rhml) [] {$k_s$};
\node (load_label) at (rhtt) [] {$P$};
\node (angle_label) at ($ (mm)!.4cm!(bar_2) $) [] {$\phi$};

\path (bar_1) -- (bar_2) [draw, very thick];
\path (bar_1) circle (.10) [fill=black];
\path (bar_2) circle (.10) [fill=black];
\path (spring_1_pin) circle (.10) [fill=black];
\path [decorate, decoration={coil, segment length = 4, amplitude=4}] (bar_2) -- (spring_1_pin) [draw, thin, stroke=black];
\path (rht) -- ($ (bar_2)!.2cm!(rht) $) [draw, -latex, ultra thick, color=black];
\path (lm) arc(0:16:2) (lm) [draw];
\path (bar_1) -- (mm) [draw, -latex];
--cycle
\end{tikzpicture}

\caption{Beam and spring simulated in example program.} \label{fig:TrussSchematic}
\end{figure}
%
The equations describing this system and results for verification were obtained
in \cite{rezaiee2010dynamic}. They include a force function, Eqn.
\ref{eqn:TrussForce}, and an analytical force derivative or stiffness, Eqn.
\ref{eqn:TrussStiffness}.
